A bootstrap-based comparison of ILI intensity thresholds from the moving epidemic and WHO methods

### 2021-01-29 Draft/Draft_MEM.tex
Using correct terminology for wILI.

We use publicly available influenza surveillance data from four countries. Data on the weekly incidence of influenza-like-illness in France, 1985--2019, were obtained from the Réseau Sentinelles web platform (INSERM/Sorbonne Université, \url{https://www.sentiweb.fr}, \citealt{Flahault2006}). Population data were obtained from Institut national de la statistique et des études économiques. Data on weekly confirmed influenza cases in Spain, 1998--2019, were extracted from graphs shown in the \textit{Informe Anual} of the \textit{Sistema de la vigilancia de gripe en Espa\~na} (\url{https://vgripe.isciii.es/}; \citealt{SVGE2019}) using the tool \textit{WebPlotDigitizer} (\url{https://apps.automeris.io/wpd/}). Weekly ILI counts from Swiss routine surveillance, collected by the Swiss Federal Office of Public Health, 2000--2016, were obtained from the R package \texttt{HIDDA.forecasting} \citep{Held2019}. Population data were obtained from the Swiss Federal Statistical Office. Weekly weighted ILI percentage rates (wILI) in the US from CDC FluView \citep{Charbonneau2019}, 1998--2017, were obtained from the CDC FluSight influenza forecasting platform (\url{https://github.com/FluSightNetwork/cdc-flusight-ensemble/}). These wILI values correspond to the percentage of general practitioner visits due to influenza-like symptoms

@@

\begin{figure}[h]
\center
\includegraphics[width=0.9\textwidth]{figure/plot_data.pdf}
\caption{Time series of influenza activity measures in four countries: Weekly ILI cases per 100,000 population in France, 1985--2019; weekly number of confirmed influenza cases per 100,000 population in Spain, 1998--2019; weekly ILI cases per 100,000 in Switzerland, 2000--2016; weekly wILI percentages in the United States, 1998--2017. Off-season weeks are omitted in the plot, with grey lines delimiting the different seasons.}
\label{fig:data}
\end{figure}

>>>>

We use publicly available influenza surveillance data from four countries. Data on the weekly incidence of influenza-like-illness in France, 1985--2019, were obtained from the Réseau Sentinelles web platform (INSERM/Sorbonne Université, \url{https://www.sentiweb.fr}, \citealt{Flahault2006}). Population data were obtained from Institut national de la statistique et des études économiques. Data on weekly confirmed influenza cases in Spain, 1998--2019, were extracted from graphs shown in the \textit{Informe Anual} of the \textit{Sistema de la vigilancia de gripe en Espa\~na} (\url{https://vgripe.isciii.es/}; \citealt{SVGE2019}) using the tool \textit{WebPlotDigitizer} (\url{https://apps.automeris.io/wpd/}). Weekly ILI counts from Swiss routine surveillance, collected by the Swiss Federal Office of Public Health, 2000--2016, were obtained from the R package \texttt{HIDDA.forecasting} \citep{Held2019}. Population data were obtained from the Swiss Federal Statistical Office. Weekly weighted ILI (wILI) data at the US national level from CDC FluView \citep{Charbonneau2019}, 1998--2017, were obtained via the CDC FluSight influenza forecasting platform (\url{https://github.com/FluSightNetwork/cdc-flusight-ensemble/}). These wILI values correspond to the fraction of general practitioner visits due to influenza-like symptoms

@@

\begin{figure}[h]
\center
\includegraphics[width=0.9\textwidth]{figure/plot_data.pdf}
\caption{Time series of influenza activity measures in four countries: Weekly ILI cases per 100,000 population in France, 1985--2019; weekly number of confirmed influenza cases per 100,000 population in Spain, 1998--2019; weekly ILI cases per 100,000 in Switzerland, 2000--2016; weekly wILI values in the United States, 1998--2017. Off-season weeks are omitted in the plot, with grey lines delimiting the different seasons.}
\label{fig:data}
\end{figure}
